---
title: "doc_track"
author: "Harshali"
date: "1/30/2016"
output: html_document
---
```{r}
library(tm)
```
The goal is to create a list having the terms, thier positions and if they are the same or changed in other documents.

Import the three text files through following code:-

```{r}
file1<-readLines("harshaliv1.txt")
file1<-gsub("[^a-zA-Z0-9]"," ",file1)
file2<-readLines("harshaliv2.txt")
file2<-gsub("[^a-zA-Z0-9]"," ",file2)
file3<-readLines("harshaliv3.txt")
file3<-gsub("[^a-zA-Z0-9]"," ",file3)
files<-data.frame(c(file1,file2,file3))
names(files)<-"documents"

```

The above command returns a list. To compare with each term we split it into single words as follows:-

```{r}

words1<-strsplit(file1," ")# returns list compares words
words2<-strsplit(file2," ")
words3<-strsplit(file3," ")

```

To convert it to character vector, we extract it from first element of list:-

```{r}
words1_char<-tolower(words1[[1]])#returns char vector and lowers the cases
words2_char<-tolower(words2[[1]])
words3_char<-tolower(words3[[1]])
```

Why convert to a corpus, isnt it simpler like this:

```{r}
setdiff(words2_char, words1_char)
intersect(words2_char, words3_char)
setdiff(words2_char, words3_char)
```

If we invert the order of vectors, we do not get the desired result,for example:
```{r}

setdiff(words3_char, words2_char)

```

The problem can be fixed by using Union as follows:

```{r}
union(setdiff(words3_char, words2_char),setdiff(words2_char, words3_char))
```

Still it returns list of words that are different in two vectors. 
I am not sure if this is the right approach to find their positions
and also in terms of semantic meaning for constructing sentences.

By using terms I intended to find the sequence of terms occuring in the text document.

```{r}
clean_data<-gsub("[^a-zA-Z0-9]"," ",files$documents)
corpus_clean <- Corpus(VectorSource(clean_data))
corpus_clean <- tm_map(corpus_clean,content_transformer(tolower)) 
corpus_clean <- tm_map(corpus_clean, removePunctuation) 
dtm<-DocumentTermMatrix(corpus_clean) 
terms<-dtm$dimnames$Terms
terms
```

Something like this:

```{r eval=TRUE}
comp.match.file1<-sapply(words1_char, function(y) grep(y,terms)[1])
comp.match.file2<-sapply(words2_char, function(y) grep(y,terms)[1])
comp.match.file3<-sapply(words3_char, function(y) grep(y,terms)[1])
```

It returns a named integer vector with the word(from the text) and the term number(from dtm)
present at that word:-

```{r}
comp.match.file1
comp.match.file2
comp.match.file3

```

Words like "my", "of", "be" lists as "NA" , I dont know why dtm ignores the words while constructing dtm.

We can solve this later, about the "my", "of", but I think you are right, it is a good idea to use a dtm, also because I think it will speed things up. The one missing element now is to figure out the position in the text of the terms. 